3D Magnetic modelling of ellipsoidal bodies

### 2017-02-09 manuscript/manuscript.tex
include particular cases of magnetization

By considering $\tilde{\mathbf{r}}$ as a point within the
volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
inside ellipsoidal bodies, we can use Eq. \ref{eq:H-tilde}
for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
inside the ellipsoidal body as follows:
\begin{equation}
\tilde{\mathbf{H}}^{\dagger} = 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:Hi-tilde}
\end{equation}
where $\mathbf{I}$ is the identity matrix and 
$\tilde{\mathbf{N}}^{\dagger}$ is a diagonal matrix
representing the transformed depolarization tensor 
evaluated within the volume $\vartheta$ of the ellipsoidal body. 
The elements of $\tilde{\mathbf{N}}^{\dagger}$ will be 
presented in a latter section.

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
For the particular case in which the susceptibility is isotropic
(Eq. \ref{eq:K-isotropic}) and $\chi << 1$, the magnetization
$\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde}) can be approximated
as follows:
\begin{equation}
\tilde{\mathbf{M}} \approx \chi \, \tilde{\mathbf{H}}_{0} \: ,
\label{eq:M-tilde-chi-H0}
\end{equation}
which is the classical equation describing the induced
magnetization in applied geophysics \citep[p. 87]{blakely1996}.
Notice that, in this particular case, the magnetization is
parallel to the inducing field $\tilde{\mathbf{H}}_{0}$.

FALAR DO CASO EM QUE A INDUCAO EH PARALELA A UM EIXO DO ELIPSOIDE

>>>>

By considering $\tilde{\mathbf{r}}$ as a point within the
volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
inside ellipsoidal bodies, we can use Eq. \ref{eq:H-tilde}
for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
inside the ellipsoidal body as follows:
\begin{equation}
\tilde{\mathbf{H}}^{\dagger} = 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:Hi-tilde}
\end{equation}
where $\mathbf{I}$ is the identity matrix and 
$\tilde{\mathbf{N}}^{\dagger}$ is a diagonal matrix
representing the transformed depolarization tensor 
evaluated within the volume $\vartheta$ of the ellipsoidal body.
For a given ellipsoid, the elements of $\tilde{\mathbf{N}}^{\dagger}$ 
are constants which are expressed in terms of the ellipsoid semi-axes.
These elements are presented in detail in a latter section.

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.

555555555555555555555555555

For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde})
can be rewritten as follows:
\begin{equation}
\tilde{\mathbf{M}} = \left[ \begin{array}{ccc}
\frac{\chi}{1 - \chi \, \tilde{n}^{\dagger}_{11}} & 0 & 0 \\
0 & \frac{\chi}{1 - \chi \, \tilde{n}^{\dagger}_{22}} & 0 \\
0 & 0 & \frac{\chi}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
\end{array} \right]
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:M-tilde-K-isotropic}
\end{equation}
where $\tilde{n}^{\dagger}_{ii}$, $i = 1, 2, 3$, are the constant
elements of the transformed depolarization tensor
$\tilde{\mathbf{N}}^{\dagger}$.
Equation \ref{eq:M-tilde-K-isotropic} reveals that,
the magnetization $\tilde{\mathbf{M}}$ is parallel to
the inducing field $\tilde{\mathbf{H}}_{0}$
is parallel to an ellipsoid axis, the magnetization is

If we additionally consider that $\chi << 1$, the magnetization
$\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde}) can be approximated
as follows:
\begin{equation}
\tilde{\mathbf{M}} \approx \chi \, \tilde{\mathbf{H}}_{0} \: ,
\label{eq:M-tilde-chi-H0}
\end{equation}
which is the classical equation describing the induced
magnetization in applied geophysics \citep[p. 87]{blakely1996}.
Notice that, in this particular case, the magnetization is
parallel to the inducing field $\tilde{\mathbf{H}}_{0}$.

555555555555555555555555555555555555555555
